### 2017-11-23 UOW_thesis_template_v2-0/thesis_template/chapters/jumpdiffEuro.tex
:art: Jeff's changes before Marianito's help

Analogous to \cite{Merton1976} and \cite{Frontczak2013}, we want to solve the problem (\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). First, we assume that the function $v_\text{e} = v_\text{e}(x,t)$ denotes the European option with an underlying that is subjected to jump-diffusion dynamics, and that is a solution to~(\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). Applying the Mellin transform of $v_\text{e}$ with respect to $x$ to (\ref{eqn:PIDE}), \eqref{eqn:PIDEcondition}, we get

@@

		&\qquad + \lambda \int_0^\infty x^{\xi-1} \left( \int_0^\infty (v_\text{e}(xy,t) - v_\text{e}(x,t))f(y) \, \d y \right) \, \d x = 0, \quad \hat v_\text{e}(\xi,T) = \hat \phi(\xi).

@@

To find $\J$, we can actually bypass the complex integral required for an inverse Mellin transform. From \eqref{eqn:JMellin}, we have

@@

where $I$ is an arbitrary interval with endpoints $a$ and $b$ with $a < b$. This specified interval can be open, half-closed or closed. For example, a call option has payoff $\phi(x) = \max(x-K,0)$ which can be formulated as

@@

There is also interest in finding an exact solution for Kou's double exponentially distributed jumps \cite{Kou2002, Kou2004} using \eqref{eqn:optionJump} and \eqref{eqn:jumpGeneral} since recent empirical studies suggest a better model for the asset process involves the jumps following a double exponential distribution. In particular, it may be of interest to see whether or not a Mellin transform route would generate a more elegant and simple solution in lieu of Kou's original solution, which involves the computation of quite complicated $Hh$ functions (see \cite[pp. 691]{Abramowitz1972}). There is also the possibility to extend \eqref{eqn:optionJump} to price American options in jump-diffusion models, which will be examined in chapter 5 of this thesis.

>>>>

Analogous to \cite{Merton1976} and \cite{Frontczak2013}, we want to solve the problem (\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). First, we assume that the function $v_\text{e} = v_\text{e}(x,t)$ denotes the European option with an underlying that is described by jump-diffusion dynamics, and that is a solution to~(\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). Applying the Mellin transform of $v_\text{e}$ with respect to $x$ to (\ref{eqn:PIDE}), \eqref{eqn:PIDEcondition}, we get

@@

		&\qquad + \lambda \int_0^\infty x^{\xi-1} \left( \int_0^\infty (v_\text{e}(xy,t) - v_\text{e}(x,t))f(y) \, \d y \right) \, \d x = 0, \\
		&\qquad \qquad \qquad \qquad \qquad \qquad \quad \hat v_\text{e}(\xi,T) = \hat \phi(\xi).

@@

As a short foreword, all derivations presented in this section are formal. To find $\J$, we can actually bypass the complex integral required for an inverse Mellin transform. From \eqref{eqn:JMellin}, we have

@@

where $I$ is an arbitrary interval with endpoints $a$ and $b > a$; the interval can be open, half-closed or closed. For example, a call option has payoff $\phi(x) = \max(x-K,0)$ which can be formulated as

@@

There is also interest in finding an exact solution for Kou's double exponentially distributed jumps \cite{Kou2002, Kou2004} using \eqref{eqn:optionJump} and \eqref{eqn:jumpGeneral} since recent empirical studies (in particular, the tests performed in~\cite{Ramezani1998}) suggest a better model for the asset process involves the jumps following a double exponential distribution. In particular, it may be of interest to see whether or not a Mellin transform route would generate a more elegant and simple solution in lieu of Kou's original solution, which involves the computation of quite complicated $Hh$ functions (see \cite[pp. 691]{Abramowitz1972}). There is also the possibility to extend \eqref{eqn:optionJump} to price American options in jump-diffusion models, which will be examined in chapter 5 of this thesis.
